

---
title: "visNetwork"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(visNetwork)
```

## R MarkdownPackage ‘visNetwork"
December 5, 2018
Title Network Visualization using 'vis.js' Library
Version 2.0.5
Date 2018-12-05
Maintainer Benoit Thieurmel <benoit.thieurmel@datastorm.fr>
Description Provides an R interface to the 'vis.js' JavaScript charting
library. It allows an interactive visualization of networks.
BugReports https://github.com/datastorm-open/visNetwork/issues
URL http://datastorm-open.github.io/visNetwork/
Depends R (>= 3.0)
Imports htmlwidgets, htmltools, jsonlite, magrittr, utils, methods,
grDevices, stats
License MIT + file LICENSE
Suggests knitr, rmarkdown, webshot, igraph, rpart, shiny,
shinyWidgets, colourpicker, sparkline, ggraph, flashClust
VignetteBuilder knitr, rmarkdown, webshot
RoxygenNote 6.0.1
NeedsCompilation no
Author Almende B.V. [aut, cph] (vis.js library in htmlwidgets/lib,
http://visjs.org, http://www.almende.com/home),
Benoit Thieurmel [aut, cre] (R interface),
Titouan Robert [aut, ctb]
Repository CRAN
Date/Publication 2018-12-05 08:40:03 UTC
R topics documented:
addExport..... . . 3
addFontAwesome.... . . . . . . 4
addIonicons..... . 5
visClusteringByColor.... . . . . 5
1
2 R topics documented:
visClusteringByConnection.... . 6
visClusteringByGroup.... . . . 7
visClusteringByHubsize.... . . 8
visClusteringOutliers.... . . . . 9
visConfigure..... . 9
visDocumentation.... . . . . . . 11
visEdges..... . . . 11
visEvents..... . . 16
visExport..... . . 20
visFit..... . . . . 21
visFocus..... . . . 22
visGetBoundingBox.... . . . . 23
visGetConnectedEdges.... . . . 24
visGetConnectedNodes.... . . . 25
visGetEdges..... . 26
visGetNodes..... . 27
visGetPositions....28
visGetScale..... . 29
visGetSelectedEdges.... . . . . 30
visGetSelectedNodes.... . . . . 31
visGetSelection....32
visGetViewPosition.... . . . . . 33
visGroups..... . . 34
visHclust..... . . 35
visHierarchicalLayout.... . . . . 37
visIgraphLayout....39
visInteraction..... 41
visLayout..... . . 44
visLegend..... . . 45
visMoveNode..... 47
visNearestNodes.... . . . . . . 48
visNetwork..... . 49
visNetwork-collapse.... . . . . 53
visNetwork-igraph.... . . . . . 55
visNetwork-shiny.... . . . . . . 57
visNetwork-treeModule.... . . . 58
visNetworkEditor.... . . . . . . 61
visNetworkEditor-module.... . 62
visNodes..... . . 64
visOptions..... . . 68
visPhysics..... . . 73
visRedraw..... . . 77
visRemoveEdges.... . . . . . . 78
visRemoveNodes.... . . . . . . 79
visSave..... . . . 80
visSelectEdges....81
visSelectNodes....82
visSetData..... . . 83
addExport 3
visSetOptions..... 84
visSetSelection....85
visSetTitle..... . . 86
visStabilize..... . 87
visStartSimulation.... . . . . . . 88
visStopSimulation.... . . . . . . 88
visStorePositions.... . . . . . . 89
visTree..... . . . 90
visTreeEditor..... 93
visUnselectAll..... 94
visUpdateEdges....95
visUpdateNodes....96
%>%..... . . . . 97
Index 98
addExport Add libraries dependencies used in export visExport
#### Description
Add libraries dependencies used in export visExport
#### Usage
<pre><code>
addExport(graph, pdf = TRUE)
</code></pre>
#### Arguments
* ``graph`` : a visNetwork object
pdf : boolean. Add jsPDF or not ?
Value
graph htmlwidget with dependencies attached.
4 addFontAwesome
addFontAwesome Use fontAwesome icons in visNetwork graph
#### Description
Add Font-Awesome for styling our graph with beautiful, professional icons. Please note that you"ll
already have these icons if using Shiny. Can also use addIonicons
#### Usage
<pre><code>
addFontAwesome(graph)
</code></pre>
#### Arguments
* ``graph`` : a visNetwork object
Value
graph htmlwidget with Font-Awesome dependencies attached.
#### Examples
```{r}
# use fontAwesome icons using groups or nodes options
# font-awesome is not part of dependencies. use addFontAwesome() if needed.
# https://fontawesome.com/v4.7.0/
# Version in package (and compatible with vis.js) : 4.7.0
# cheatsheet available in package:
# system.file("fontAwesome/Font_Awesome_Cheatsheet.pdf", package = "visNetwork")
# definition in groups
nodes <- data.frame(id = 1:3, group = c("B", "A", "B"))
edges <- data.frame(from = c(1,2), to = c(2,3))
visNetwork(nodes, edges) %>%
visGroups(groupname = "A", shape = "icon", icon = list(code = "f0c0", size = 75)) %>%
visGroups(groupname = "B", shape = "icon", icon = list(code = "f007", color = "red")) %>%
addFontAwesome()
```
```{r}
# definition in nodes
nodes <- data.frame(id = 1:3, shape = "icon", icon.face = 'FontAwesome',
icon.code = "f0c0")
edges <- data.frame(from = c(1,2), to = c(1,3))
visNetwork(nodes, edges) %>%
addFontAwesome()
```
addIonicons Use Ionicons in visNetwork graph
#### Description
Add Ionicons for styling our graph with beautiful, professional icons. See Cheatsheet to get CSS
content code. Can also use addFontAwesome
#### Usage
<pre><code>
addIonicons(graph)
</code></pre>
#### Arguments
* ``graph`` : a visNetwork object
* ``Value`` : graph htmlwidget with Ionicons dependencies attached.
#### Examples
```{r}
nodes <- data.frame(id = 1:3, group = c("B", "A", "B"))
edges <- data.frame(from = c(1,2), to = c(2,3))
visNetwork(nodes, edges) %>%
visGroups(groupname = "A", shape = "icon",
icon = list(face ='Ionicons', code = "f101", size = 75)) %>%
visGroups(groupname = "B", shape = "icon",
icon = list(face ='Ionicons', code = "f100", color = "red")) %>%
addIonicons()
```
visClusteringByColor Network visualization clustering options - by color
#### Description
Network visualization clustering options - by color.
#### Usage
<pre><code>
visClusteringByColor(graph, colors, label = "Cluster on color : ",
shape = "database", force = FALSE)
</code></pre>
#### Arguments
* ``graph`` : a visNetwork object
* ``colors`` : Character/vector. colors we want to cluster
label : Character. Label put before value(s). See example
shape : Character. Shape of cluster(s) if different shapes between nodes or force = T.
"database" per default
force : If force = FALSE, Set shape of nodes if all equal, else directly defaut shape
#### Examples
```{r}
set.seed(124)
nodes <- data.frame(id = 1:10, color = c(rep("blue", 6), rep("red", 3), rep("green", 1)))
edges <- data.frame(from = round(runif(6)*10), to = round(runif(6)*10))
visNetwork(nodes, edges) %>%
visClusteringByColor(colors = c("blue"))
nodes <- data.frame(id = 1:10, label = paste("Label", 1:10),
group = sample(c("A", "B"), 10, replace = TRUE))
edges <- data.frame(from = c(2,5,10), to = c(1,2,10))
visNetwork(nodes, edges) %>%
visGroups(groupname = "A", color = "red", shape = "square") %>%
visGroups(groupname = "B", color = "yellow", shape = "triangle") %>%
visClusteringByColor(colors = c("red"), label = "With color ") %>%
visClusteringByGroup(groups = c("B"), label = "Group : ") %>%
visLegend()
visNetwork(nodes, edges) %>%
visGroups(groupname = "A", color = "red", shape = "triangle") %>%
visGroups(groupname = "B", color = "yellow", shape = "triangle") %>%
visClusteringByGroup(groups = c("A","B")) %>%
visLegend()
```
visClusteringByConnection
Network visualization clustering options - by node id
#### Description
Network visualization clustering options - by node id
#### Usage
<pre><code>
visClusteringByConnection(graph, nodes)
visClusteringByGroup 7
</code></pre>
#### Arguments
* ``graph`` : a visNetwork object
nodes : Character/vector. id of nodes we want to cluster
#### Examples
```{r}
set.seed(124)
nodes <- data.frame(id = 1:10, color = c(rep("blue", 6), rep("red", 3), rep("green", 1)))
edges <- data.frame(from = round(runif(6)*10), to = round(runif(6)*10))
visNetwork(nodes, edges) %>%
visClusteringByConnection(nodes = 9)
```
visClusteringByGroup Network visualization clustering options - by group
#### Description
Network visualization clustering options - by group.
#### Usage
<pre><code>
visClusteringByGroup(graph, groups, label = "Cluster on group : ",
shape = "database", color = "grey", force = FALSE, scale_size = TRUE)
</code></pre>
#### Arguments
* ``graph`` : a visNetwork object
groups : Character/vector. groups we want to cluster
label : Character. Label put before value(s). See example
shape : Character. Shape of cluster(s) if different shapes between nodes or force = T.
"database" per default
color : Character. Color of cluster(s) if different colors between nodes or force = T.
"grey" per default
force : If force = FALSE, Set shape and color of nodes if all equal, else directly
defaut shape and color
scale_size : Set size based on cluster population ? Default to TRUE.
8 visClusteringByHubsize
#### Examples
```{r}
nodes <- data.frame(id = 1:10, label = paste("Label", 1:10),
group = sample(c("A", "B"), 10, replace = TRUE))
edges <- data.frame(from = c(2,5,10), to = c(1,2,10))
visNetwork(nodes, edges) %>%
visGroups(groupname = "A", color = "red", shape = "database") %>%
visGroups(groupname = "B", color = "yellow", shape = "triangle") %>%
visClusteringByGroup(groups = c("B"), label = "Group : ",
shape = "ellipse", color = "blue", force = TRUE) %>%
visLegend()
```
visClusteringByHubsize
Network visualization clustering options - by hubsize
#### Description
Network visualization clustering options - by hubsize
#### Usage
<pre><code>
visClusteringByHubsize(graph, size = NULL)
</code></pre>
#### Arguments
* ``graph`` : a visNetwork object
size : Integer. This method checks all nodes in the network and those with a equal or
higher amount of edges than specified with size argument. If size is null (defaut),
the size will be determined as the average value plus two standard deviations.
#### Examples
```{r}
set.seed(124)
nodes <- data.frame(id = 1:10, color = c(rep("blue", 6), rep("red", 3), rep("green", 1)))
edges <- data.frame(from = round(runif(6)*10), to = round(runif(6)*10))
visNetwork(nodes, edges) %>%
visClusteringByHubsize()
visNetwork(nodes, edges) %>%
visClusteringByHubsize(size = 2)
```
visClusteringOutliers Network visualization clustering options - outliers
#### Description
Network visualization clustering options - outliers
#### Usage
<pre><code>
visClusteringOutliers(graph, clusterFactor = 0.9, stabilize = FALSE)
</code></pre>
#### Arguments
* ``graph`` : a visNetwork object
clusterFactor : Number, from 0 to 1. 0.9 by default
stabilize : Boolean, default to false
#### Examples
```{r}
nodes <- data.frame(id = 1:10)
edges <- data.frame(from = c(1,1,10,2,6,7,8,9,10),
to = c(2,3,4,5,2,5,6,7,9))
visNetwork(nodes, edges) %>%
visClusteringOutliers(1)
```
