
---
title: "visNetwork"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(visNetwork)
```
visExport Network export configuration
#### Description
Network export configuration. This function only work within shiny or a web browser.
#### Usage
<pre><code>
visExport(graph, type = "png", name = "network",
label = paste0("Export as ", type), background = "#fff",
float = "right", style = NULL, loadDependencies = TRUE, ...)
</code></pre>
#### Arguments
* ``graph`` : a visNetwork object
* ``type`` :   Type of export. One of "png" (default), "jpeg" or "pdf"
name : name of imgage, default to "network"
label : Label on button, default to "Export as png/jpeg/pdf"
background : background color, default to white (#fff). Work only if network background is
transparent.
float : button postion, default to "right"
style : button css style.
loadDependencies
/ Boolean. TRUE by default. Load libraries for export (fileSaver, Blob, canvastoBlob,
html2canvas, jsPDF)
... : arguments for addExport
#### References
See online documentation http://datastorm-open.github.io/visNetwork/
See Also
visSave
#### Examples
```{r}
## Not run:
nodes <- data.frame(id = 1:3, group = c("B", "A", "B"))
edges <- data.frame(from = c(1,2), to = c(2,3))
visNetwork(nodes, edges) %>%
visGroups(groupname = "A", color = "red") %>%
visFit 21
visGroups(groupname = "B", color = "lightblue") %>%
visLegend() %>% visExport()
visNetwork(nodes, edges) %>%
visGroups(groupname = "A", color = "red") %>%
visGroups(groupname = "B", color = "lightblue") %>%
visLegend() %>% visExport(type = "jpeg", name = "export-network",
float = "left", label = "Save network", background = "purple", style= "")
## End(Not run)
```
