---
title: "``visFit``: Network visualization fit method"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(visNetwork)
```

#### Description
For use ``fit()`` method in a shiny app. For full documentation, have a look at visDocumentation.

#### Usage
<pre><code>
visFit(graph, nodes = NULL, animation = list(duration = 1500, easingFunction = "easeInOutQuad"))
</code></pre>

#### Arguments
* ``graph`` : a visNetworkProxy object
* ``nodes`` : NULL for all nodes (Default), or a vector of nodes id
* ``animation`` : Optional. List. 



#### Examples
```{r}
## Not run:
# have a look to :
shiny::runApp(system.file("shiny", package = "visNetwork"))
## End(Not run)
```

#### Animation

For animation you can define the duration (in milliseconds) and
easing function manually. Available are: linear, easeInQuad, easeOutQuad, easeInOutQuad, easeInCubic, easeOutCubic, easeInOutCubic, easeInQuart, easeOutQuart, easeInOutQuart, easeInQuint, easeOutQuint, easeInOutQuint. Default
to list(duration = 1500, easingFunction = "easeInOutQuad")


#### References
See online documentation http://datastorm-open.github.io/visNetwork/


#### See Also
visNodes for nodes options, visEdges for edges options, visGroups for groups options, visLegend
for adding legend, visOptions for custom option, visLayout & visHierarchicalLayout for layout,
visPhysics for control physics, visInteraction for interaction, visNetworkProxy & visFocus & visFit
for animation within shiny, visDocumentation, visEvents, visConfigure ...
