---
title: "``visGetNodes``:  Function to get nodes data, with shiny only."
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(visNetwork)
```


#### Description
Function to get nodes data, with shiny only.

#### Usage
<pre><code>
visGetNodes(graph, input = paste0(graph$id, "_nodes"), addCoordinates = T)
</code></pre>

#### Arguments
* ``graph`` : a visNetworkProxy object
* ``input`` : name of shiny input created. Default to paste0(graph$id, "_nodes")
* ``addCoordinates`` :   Boolean. Add coordinates to nodes data ? Default to TRUE.

#### References
See online documentation http://datastorm-open.github.io/visNetwork/

#### See Also
visNodes for nodes options, visEdges for edges options, visGroups for groups options, visLegend for adding legend, visOptions for custom option, visLayout & visHierarchicalLayout for layout, visPhysics for control physics, visInteraction for interaction, visNetworkProxy & visFocus & visFit for animation within shiny, visDocumentation, visEvents, visConfigure ...

#### Examples

```{r}
## Not run:
# have a look to :
shiny::runApp(system.file("shiny", package = "visNetwork"))
## End(Not run)
```
