---
title: "``visGetSelectedNodes``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(visNetwork)
```
Function to get selected nodes, with shiny only.
#### Description
Function to get selected nodes, with shiny only. Returns a vector of selected node ids.

#### Usage

<pre><code>
visGetSelectedNodes(graph, input = paste0(graph$id, "_selectedNodes"))
</code></pre>

#### Arguments
* ``graph`` : a visNetworkProxy object
* ``input`` : name of shiny input created. Default to ``paste0(graph$id, "_selectedNodes")``


#### Examples
```{r}
## Not run:
# have a look to :
shiny::runApp(system.file("shiny", package = "visNetwork"))
## End(Not run)
```

#### References
See online documentation http://datastorm-open.github.io/visNetwork/

#### See Also
visNodes for nodes options, visEdges for edges options, visGroups for groups options, visLegend
for adding legend, visOptions for custom option, visLayout & visHierarchicalLayout for layout,
visPhysics for control physics, visInteraction for interaction, visNetworkProxy & visFocus & visFit
for animation within shiny, visDocumentation, visEvents, visConfigure ...