---
title: "``visGroups ``: Network visualization groups options."
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(visNetwork)
```


#### Description
Network visualization groups options. For full documentation, have a look at visDocumentation.

#### Usage
<pre><code>
visGroups(graph, useDefaultGroups = TRUE, groupname = NULL, ...)
</code></pre>

#### Arguments
* ``graph`` : a visNetwork object
* ``useDefaultGroups`` : Boolean. Default to true. If your nodes have groups defined that are not in the Groups module, the module loops over the groups it does have, allocating one
for each unknown group. When all are used, it goes back to the first group. By setting this to false, the default groups will not be used in this cycle.
* ``groupname`` : String. Name of target group.
* ... : visNodes. You can add multiple groups containing styling information that applies to a certain subset of groups. All options described in the nodes module
that make sense can be used here (you’re not going to set the same id or x,y position for a group of nodes)


#### Examples
```{r}
nodes <- data.frame(id = 1:10, label = paste("Label", 1:10),
group = sample(c("A", "B"), 10, replace = TRUE))
edges <- data.frame(from = c(2,5,10), to = c(1,2,10))
visNetwork(nodes, edges) %>%
visLegend() %>%
visGroups(groupname = "A", color = "red", shape = "database") %>%
visGroups(groupname = "B", color = "yellow", shape = "triangle")
```

#### References
See online documentation http://datastorm-open.github.io/visNetwork/
See Also
visNodes for nodes options, visEdges for edges options, visGroups for groups options, visLegend
for adding legend, visOptions for custom option, visLayout & visHierarchicalLayout for layout,
visPhysics for control physics, visInteraction for interaction, visNetworkProxy & visFocus & visFit
for animation within shiny, visDocumentation, visEvents, visConfigure ...
