---
title: "visExport :  Network export configuration"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(visNetwork)
```
visGetBoundingBox Method getBoundingBox, with shiny only.

#### Description

Method getBoundingBox, with shiny only. Returns a bounding box for the node including label in
the format. These values are in canvas space.

#### Usage
<pre><code>
visGetBoundingBox(graph, id, input = paste0(graph$id, "_boundingBox"))
</code></pre>

#### Arguments
* ``graph`` : a visNetworkProxy object
* ``id`` : a node or edge id
* ``input`` : name of shiny input created. Default to paste0(graph$id, "_boundingBox")

#### References
See online documentation http://datastorm-open.github.io/visNetwork/

#### See Also
visNodes for nodes options, visEdges for edges options, visGroups for groups options, visLegend
for adding legend, visOptions for custom option, visLayout & visHierarchicalLayout for layout,
visPhysics for control physics, visInteraction for interaction, visNetworkProxy & visFocus & visFit
for animation within shiny, visDocumentation, visEvents, visConfigure ...

#### Examples
```{r}
## Not run:
# have a look to :
shiny::runApp(system.file("shiny", package = "visNetwork"))
## End(Not run)
```
