
---
title: "``visEdges``: Network visualization edges options"
output: html_document
---
 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(visNetwork)
```
visGetViewPosition 33
visGetViewPosition Function to get current view position, with shiny only.
#### Description
Function to get current view position, with shiny only. Returns the current central focus point of the
view.
#### Usage
<pre><code>
visGetViewPosition(graph, input = paste0(graph$id, "_viewPosition"))
</code></pre>
#### Arguments
* ``graph`` : a visNetworkProxy object
* ``input`` : name of shiny input created. Default to paste0(graph$id, "_viewPosition")
#### References
See online documentation http://datastorm-open.github.io/visNetwork/
See Also
visNodes for nodes options, visEdges for edges options, visGroups for groups options, visLegend
for adding legend, visOptions for custom option, visLayout & visHierarchicalLayout for layout,
visPhysics for control physics, visInteraction for interaction, visNetworkProxy & visFocus & visFit
for animation within shiny, visDocumentation, visEvents, visConfigure ...
#### Examples
```{r}
## Not run:
# have a look to :
shiny::runApp(system.file("shiny", package = "visNetwork"))
## End(Not run)
