---
title: "``visHclust``:   Visualize Hierarchical cluster analysis."
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(visNetwork)
```



#### Description
Visualize Hierarchical cluster analysis hclust. This function compute distance using dist, and Hierarchical cluster analysis using hclust (from stats package or flashClust if installed), and render the tree with visNetwork, adding informations. Can also be called on a hclust or dist object.
Needed packages : sparkline (graphics on tooltip), ggraph, igraph, flashClust

#### Usage
<pre><code>
visHclust(object, ...)
## Default S3 method:
visHclust(object, ...)

## S3 method for class 'data.frame'
visHclust(object, main = "", submain = "", footer = "", distColumns = NULL, distMethod = "euclidean",
hclustMethod = "complete", cutree = 0, tooltipColumns = 1:ncol(object),
colorEdges = "black", colorGroups = substr(rainbow(cutree), 1, 7),
highlightNearest = TRUE, horizontal = FALSE, minNodeSize = 50,
maxNodeSize = 200, nodesPopSize = TRUE, height = "600px", width = "100%", export = TRUE, ...)

## S3 method for class 'dist'
visHclust(object, data = NULL, main = "", submain = "",
footer = "", cutree = 0, hclustMethod = "complete",
tooltipColumns = if (!is.null(data)) { 1:ncol(data) } else { NULL },
colorEdges = "black", colorGroups = substr(rainbow(cutree), 1, 7),
highlightNearest = TRUE, horizontal = FALSE, minNodeSize = 50,
maxNodeSize = 200, nodesPopSize = TRUE, height = "600px",
width = "100%", export = TRUE, ...)
## S3 method for class 'hclust'
visHclust(object, data = NULL, main = "", submain = "",
footer = "", cutree = 0, tooltipColumns = if (!is.null(data)) {
1:ncol(data) } else { NULL }, colorEdges = "black",
colorGroups = substr(rainbow(cutree), 1, 7), highlightNearest = TRUE,
horizontal = FALSE, minNodeSize = 50, maxNodeSize = 200,
nodesPopSize = TRUE, height = "600px", width = "100%", export = TRUE,
...)
</code></pre>

#### Arguments

* ``object`` hclust | dist | data.frame.
* ``...``: Don’t use
* ``main``: Title. See visNetwork
* ``submain``: Subtitle. See visNetwork
* ``footer``: Footer. See visNetwork
* ``distColumns``: numeric, indice of columns used for compute distance. If NULL (default), keep all numeric and integer columns. If Not NULL, keep only numeric and integer columns
* ``distMethod``: character, the distance measure to be used for dist function. Default to ’euclidean’.
* hclustMethod character, the agglomeration method to be used for hclust function. Default to ’complete’.
* ``cutree`` :   numeric or integer, desired number of groups. Default to 0.
* tooltipColumns numeric, adding mini-graphics in tooltips using sparkline ? Indice of columns used in tooltip. All by default. So,`` we add boxplot / pie focus on sub-population
* ``vs``: all population using sparkline package. NULL to disable.
* ``colorEdges``: character, color of edges. Default to ’black’.
* colorGroups character, color for group in hexa ("#00FF00"). Default rainbow.
* highlightNearest boolean, highlight sub-tree on click ? Default to TRUE.
* ``horizontal`` :  boolean, default to FALSE
* minNodeSize numeric, in case of nodesPopSize, minimum size of a node. Defaut to 50. Else
minNodeSize + maxNodeSize / 2.
maxNodeSize numeric, in case of nodesPopSize, maximum size of a node. Defaut to 200.
Else minNodeSize + maxNodeSize / 2.
* nodesPopSize boolean, nodes sizes depends on population ? Default to TRUE.
* ``height`` :    character, default to "600px"
* ``width `` :  character, default to "100%"
* ``export`` :  boolean, add button for export. Default to TRUE
* data data.frame, data.frame with data. Only for hclust or dist object.

#### Examples

```{r}
## Not run:
#--------------
# data.frame
#--------------
# default call on data.frame
visHclust(iris, cutree = 3, colorEdges = "red")
# update some parameters
visHclust(iris, cutree = 3, tooltipColumns = c(1, 5),
colorGroups = c("red", "blue", "green"), horizontal = TRUE)
```
```{r}
# no graphics on tooltip
visHclust(iris, cutree = 3, tooltipColumns = NULL,
main = "Hclust on iris")
# Title(s)
visHclust(iris, cutree = 3, main ="My_title",
submain = "My_sub_title", footer = "My_footer")
```
```{r}
# Export
visHclust(iris, cutree = 3, export = TRUE)
# update group / individual nodes
visHclust(iris, cutree = 8) %>%
visGroups(groupname = "group", color ="black",
shape = "triangleDown", size = 75) %>%
visGroups(groupname = "individual",
font = list(size = 150),
color = list(background = "white", border = "purple",
highlight = "#e2e9e9", hover = "orange"), shape = "box")
```
```{r}
#--------------
# dist
#--------------
# without adding data & info in tooltip
visHclust(dist(iris[,1:4]), cutree = 3)
# adding data & info in tooltip
visHclust(dist(iris[,1:4]), cutree = 3, data = iris)
#--------------
# hclust
#--------------
# without adding data & info in tooltip
visHclust(hclust(dist(iris[,1:4])), cutree = 3)
# adding data & info in tooltip
visHclust(hclust(dist(iris[,1:4])), cutree = 3, data = iris)
## End(Not run)
```
