---
title: "``visMoveNode  ``:  Network visualization moveNode method"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(visNetwork)
```

#### Description
For use ``moveNode()`` method in a shiny app. For full documentation, have a look at visDocumentation.

#### Usage
<pre><code>
visMoveNode(graph, id, x, y)
</code></pre>

#### Arguments
* ``graph`` : a visNetworkProxy object
* ``id`` : a node id
* ``x`` : Number. x position, in canvas space
* ``y`` : Number. y position, in canvas space

#### Examples
```{r}
# have a look to :
shiny::runApp(system.file("shiny", package = "visNetwork"))

```
#### References
See online documentation http://datastorm-open.github.io/visNetwork/

#### See Also
visNodes for nodes options, visEdges for edges options, visGroups for groups options, visLegend for adding legend, visOptions for custom option, visLayout & visHierarchicalLayout for layout, visPhysics for control physics, visInteraction for interaction, visNetworkProxy & visFocus & visFit for animation within shiny, visDocumentation, visEvents, visConfigure ...
