---
title: "``visEdges``: Network visualization edges options"
output: html_document
---
 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(visNetwork)
```

visNetwork-treeModule Module shiny for visualize and customize a rpart tree
#### Description
Needed packages : shiny, rpart, colourpicker, shinyWidgets, sparkline
#### Usage
<pre><code>
visTreeModuleServer(input, output, session, data, tooltip_data = NULL,
tooltipColumns = "", main = "", submain = "", footer = "",
direction = "UD", fallenLeaves = FALSE, rules = TRUE,
simplifyRules = TRUE, shapeVar = "dot", shapeY = "square",
colorVar = NULL, colorY = NULL, colorEdges = "#8181F7",
  nodesFontSize = 16, edgesFontSize = 14, edgesFontAlign = "horizontal",
visNetwork-treeModule 59
legend = TRUE, legendNodesSize = 22, legendFontSize = 16,
legendWidth = 0.1, legendNcol = 1, legendPosition = "left",
nodesPopSize = FALSE, minNodeSize = 15, maxNodeSize = 30,
highlightNearest = list(enabled = TRUE, degree = list(from = 50000, to = 0),
hover = FALSE, algorithm = "hierarchical"), collapse = list(enabled = TRUE,
fit = TRUE, resetHighlight = TRUE, clusterOptions = list(fixed = TRUE, physics
= FALSE)), updateShape = TRUE, tooltipDelay = 500, digits = 3,
height = 650, width = "100%", export = TRUE)
visTreeModuleUI(id, rpartParams = TRUE, visTreeParams = TRUE,
quitButton = FALSE)
</code></pre>
#### Arguments
input list shiny input
output list, shiny output
session list, shiny session
data reactive, a data.frame or a rpart result. Must be a reactive object
tooltip_data reactive, a data.frame. if data is a rpart, data.frame used to build tree in
order to plot sparkline
tooltipColumns numeric, indice of columns used in tooltip. All by default. So, we add boxplot
/ pie focus on sub-population vs all population using sparkline package. NULL
to disable.
main Title. See visNetwork
submain Subtitle. See visNetwork
footer Footer. See visNetwork
direction character, The direction of the hierarchical layout. The available options are:
UD, DU, LR, RL. To simplify: up-down, down-up, left-right, right-left. Default
UD. See visHierarchicalLayout
fallenLeaves boolean leaf nodes at the bottom of the graph ? Default to FALSE
rules boolean, add rules in tooltips ? Default to TRUE
simplifyRules boolean, simplify rules writing
shapeVar character, shape for variables nodes See visNodes
shapeY character, shape for terminal nodes See visNodes
colorVar character, colors to use or data.frame To set color of variables. 2 columns :
-  "variable" : names of variables
-  "color" : colors (in hexa). See examples
colorY if classification tree : character colors to use or data.frame 2 columns :
-  "modality" : levels of Y
-  "color" : colors (in hexa)
if regression tree : character, 2 colors (min and max, in hexa)
colorEdges character, color of edges, in hexa. Default to #8181F7
60 visNetwork-treeModule
nodesFontSize numeric, size of labels of nodes. Default to 16
edgesFontSize numeric, size of labels of edges Default to 14
edgesFontAlign character, for edges only. Default tp ’horizontal’. Possible options: ’horizontal’
(Default),’top’,’middle’,’bottom’. See visEdges
legend boolean, add legend ? Default TRUE. visLegend
legendNodesSize
numeric, size of nodes in legend. Default to 22
legendFontSize numeric, size of labels of nodes in legend. Default to 16
legendWidth numeric, legend width, between 0 and 1. Default 0.1
legendNcol numeric, number of columns in legend. Default 1
legendPosition character, one of "left" (Default) or "right"
nodesPopSize boolean, nodes sizes depends on population ? Default to FALSE
minNodeSize numeric, in case of nodesPopSize, minimum size of a node. Defaut to 15. Else,
nodes size is minNodeSize + maxNodeSize / 2
maxNodeSize numeric, in case of nodesPopSize, maximum size of a node. Defaut to 30.
Else, nodes size is minNodeSize + maxNodeSize / 2
highlightNearest
list, Highlight nearest nodes. See visOptions
collapse list, collapse or not using double click on a node ? See visOptions
updateShape boolean, in case of collapse, udpate cluster node shape as terminal node ? Default
to TRUE
tooltipDelay numeric, delay for tooltips in millisecond. Default 500
digits numeric, number of digits. Default to 3
* ``height`` :    character, default to "600px"
* ``width `` :  character, default to "100%"
* ``export`` :  boolean, add export button. Default to TRUE
id character id of module, linked to visTreeModuleServer
rpartParams boolean, add tabs for rpart parameters (in case of data.frame in input)
visTreeParams boolean, add tabs for visTree parameters. Default to TRUE. Force to TRUE if
rpartParams
quitButton boolean, add a button to quit module and get back network in R ?
#### References
See online documentation http://datastorm-open.github.io/visNetwork/
#### Examples
```{r}
## Not run:
require(rpart)
# simple module editor on rpart
visNetworkEditor 61
data <- iris
shiny::shinyApp(ui = shiny::fluidPage(
visTreeModuleUI(id = "id1", rpartParams = FALSE, visTreeParams = FALSE)),
server = function(input, output, session) {
shiny::callModule(visTreeModuleServer, "id1", data = shiny::reactive(rpart(data)))
})
# full module editor on rpart + data.frame for sparkline
data <- iris
shiny::shinyApp(ui = shiny::fluidPage(
visTreeModuleUI(id = "id1", rpartParams = FALSE, visTreeParams = TRUE)),
server = function(input, output, session) {
shiny::callModule(visTreeModuleServer, "id1", data = shiny::reactive(rpart(data)),
tooltip_data = data)
})
# module on data.frame
shiny::shinyApp(ui = shiny::fluidPage(visTreeModuleUI(id = "id1",
rpartParams = TRUE)),
server = function(input, output, session) {
shiny::callModule(visTreeModuleServer, "id1", data = shiny::reactive(data))
})
# multiple modules
shiny::shinyApp(ui =
navbarPage("Menu",shiny::tabPanel(
"tt1",shiny::fluidPage(visTreeModuleUI(id = "id1",
rpartParams = TRUE,
visTreeParams = TRUE))
),
shiny::tabPanel(
"tt2",shiny::fluidPage(visTreeModuleUI(id = "id2",
rpartParams = FALSE,
visTreeParams = FALSE)))
),
server = function(input, output, session) {
shiny::callModule(visTreeModuleServer, "id1", data = shiny::reactive(iris))
shiny::callModule(visTreeModuleServer, "id2", data = shiny::reactive(rpart(iris)))
})
## End(Not run)
```

