---
title: "``visNearestNodes ``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(visNetwork)
```

#### Description
Function to nearest nodes of a target node, with shiny only.
#### Usage
<pre><code>
visNearestNodes(graph, target, maxpoints = 5, addDist = T)

</code></pre>

#### Arguments

* ``graph`` : a visNetworkProxy object
* ``target`` : name of shiny input returning target node id
* ``maxpoints`` : Number of nearest nodes. Default to 5
* ``addDist`` : If TRUE, add a column named dist_ that contains the distance from the coordinate to the point, in pixels.

#### Examples
```{r}
# have a look to :
shiny::runApp(system.file("shiny", package = "visNetwork"))
```

#### References
See online documentation http://datastorm-open.github.io/visNetwork/

#### See Also
visNodes for nodes options, visEdges for edges options, visGroups for groups options, visLegend
for adding legend, visOptions for custom option, visLayout & visHierarchicalLayout for layout,
visPhysics for control physics, visInteraction for interaction, visNetworkProxy & visFocus & visFit
for animation within shiny, visDocumentation, visEvents, visConfigure ...