---
title: "``visNetwork-shiny ``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(visNetwork)
```



Shiny bindings for visNetwork
#### Description
Output and render functions for using visNetwork within Shiny applications and interactive Rmd
documents. With visNetworkProxy, you can update your network without redraw in shiny.

#### Usage

<pre><code>
visNetworkOutput(outputId, width = "100%", height = "400px")
renderVisNetwork(expr, env = parent.frame(), quoted = FALSE)
visNetworkProxy(shinyId, session = shiny::getDefaultReactiveDomain())
</code></pre>

#### Arguments

* outputId : output variable to read from width, height Must be a valid CSS unit (like "100%", "400px", "auto") or a number, which will be coerced to a string and have "px" appended.
* expr An expression that generates a visNetwork
* env The environment in which to evaluate expr.
* quoted Is expr a quoted expression (with ``quote()``)? This is useful if you want to save an expression in a variable.
* shinyId single-element character vector indicating the shiny output ID of the network to modify
* session the Shiny session object to which the map belongs; usually the default value will suffice

#### Examples
```{r}
## Not run:
# have a look to :
shiny::runApp(system.file("shiny", package = "visNetwork"))
## End(Not run)
```

Details
With visNetworkProxy, you can update your network and use various methods :
-  "all ’visNetwork’ functons" : visOptions, visNodes, visEdges, visPhysics, visEvents,
...
-  visFocus : Focus to one or more nodes
-  visFit : Set view on a set of nodes
-  visUpdateNodes : Update and add nodes
-  visUpdateEdges : Update and add edges
-  visRemoveNodes : Remove nodes
-  visRemoveEdges : Remove edges
-  visSelectNodes :Select nodes
-  visSelectEdges : Select edges
-  visGetNodes : Get nodes dataset
-  visGetEdges : Get edges dataset
-  visSetSelection : Select edges/nodes
-  visNearestNodes : Get nearest nodes
-  visCollapse : Collapse nodes
-  visUncollapse : Uncollpase nodes
-  visSetTitle : Set and update main, submain, footer
-  and also... : visGetSelectedEdges, visGetSelectedNodes, visGetSelection, visGetConnectedEdges,
visGetConnectedNodes, visRedraw, visStabilize, visSetData, visGetPositions, visMoveNode,
visUnselectAll, visGetScale, visGetBoundingBox, visGetViewPosition,visSetOptions
#### References
See online documentation http://datastorm-open.github.io/visNetwork/