---
title: "`` visNodes ``: Network visualization nodes options"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(visNetwork)
```



#### Description
Network visualization nodes options. For full documentation, have a look at visDocumentation.
#### Usage
<pre><code>
visNodes(graph, id = NULL, shape = NULL, size = NULL, title = NULL, value = NULL, x = NULL, y = NULL, label = NULL, level = NULL, group = NULL, hidden = NULL, image = NULL, mass = NULL, physics = NULL, borderWidth = NULL, borderWidthSelected = NULL,
brokenImage = NULL, labelHighlightBold = NULL, color = NULL, fixed = NULL, font = NULL, icon = NULL, shadow = NULL,
scaling = NULL, shapeProperties = NULL, heightConstraint = NULL, widthConstraint = NULL, margin = NULL, chosen = NULL)
</code></pre>
#### Arguments
* ``graph`` : a visNetwork object
id : String. Default to undefined. The id of the node. The id is mandatory for nodes
and they have to be unique. This should obviously be set per node, not globally.
shape : String. Default to ’ellipse’. The shape defines what the node looks like. There
are two types of nodes. One type has the label inside of it and the other type
has the label underneath it. The types with the label inside of it are: ellipse,
circle, database, box, text. The ones with the label outside of it are: image,
circularImage, diamond, dot, star, triangle, triangleDown, square and icon.
* size : Number. Default to 25. The size is used to determine the size of node shapes
that do not have the label inside of them. These shapes are: image, circularImage,
diamond, dot, star, triangle, triangleDown, square and icon
* title : String or Element. Default to undefined. Title to be displayed when the user
hovers over the node. The title can be an HTML element or a string containing
plain text or HTML.
* value : Number. Default to undefined. When a value is set, the nodes will be scaled
using the options in the scaling object defined above.
* x : Number. Default to undefined. This gives a node an initial x position. When using the hierarchical layout, either the x or y position is set by the layout engine depending on the type of view. The other value remains untouched. When using
stabilization, the stabilized position may be different from the initial one. To
lock the node to that position use the physics or fixed options.
* y : Number. Default to undefined. This gives a node an initial y position. When
using the hierarchical layout, either the x or y position is set by the layout engine
depending on the type of view. The other value remains untouched. When using
stabilization, the stabilized position may be different from the initial one. To
lock the node to that position use the physics or fixed options.

* label : String. Default to undefined. The label is the piece of text shown in or under
the node, depending on the shape.
* level : Number. Default to undefined. When using the hierarchical layout, the level determines where the node is going to be positioned.
* group : String. Default to undefined. When not undefined, the group of node(s)
* hidden : Boolean. Default to false. When true, the node will not be shown. It will still
be part of the physics simulation though!
* image : List or String. Default to undefined. When the shape is set to image or circularImage,
this option should be the URL to an image. If the image cannot be
found, the brokenImage option can be used.
-  "unselected" : String. Unselected (default) image URL.
-  "selected" : String. Selected image URL.
mass : Number. Default to 1. The barnesHut physics model (which is enabled by default) is based on an inverted gravity model. By increasing the mass of a node, you increase it’s repulsion. Values lower than 1 are not recommended.
physics : Boolean. Default to true. When false, the node is not part of the physics
simulation. It will not move except for from manual dragging.
border* ``width`` :   Number. Default to 1. The width of the border of the node when it is not selected, automatically limited by the width of the node.
borderWidthSelected
: Number. Default to 2. The width of the border of the node when it is selected.
If left at undefined, double the borderWidth will be used.
brokenImage : String. Undefined. When the shape is set to image or circularImage, this option
can be an URL to a backup image in case the URL supplied in the image option
cannot be resolved
labelHighlightBold
: Boolean. Default to true. Determines whether or not the label becomes bold
when the node is selected.
color : String | named list. Color for the node. Can be ’rgba(120,32,14,1)’, ’#97C2FC’
(hexa notation on 7 char without transparency) or ’red’. Can be just one color,
or a list with several elements :
-  "background" : String. Default to ’#97C2FC’. Background color for the
node.
-  "border" : String. Default to ’#2B7CE9’. Border color for the node.
-  "highlight" : String | named list, Color of the node when selected.
 - "background" : String. Default to ’#97C2FC’. Background color for
the node when selected.
 - "border" : String. Default to ’#2B7CE9’. Border color for the node
when selected.
-  "hover" : named list, when the hover option is enabled
 - "background" : String. Default to ’#2B7CE9’. Border color of the
node when selected.
 - "border" : String. Default to ’#2B7CE9’. Border color of the node
when the node is hovered over and the hover option is enabled.
66 visNodes
fixed : Boolean | named list. Default to false. When true, the node will not move but
IS part of the physics simulation. When defined as an list, movement in either
X or Y direction can be disabled.
-  "x" : Boolean. When true, the node will not move in the X direction.
-  "y" : Boolean. When true, the node will not move in the Y direction.
font : Named list or String. This object defines the details of the label. A shorthand
is also supported in the form ’size face color’ for example: ’14px arial red’
-  "color" : String. Default to ’#343434’. Color of the label text.
-  "size" : Number. Default to 14. Size of the label text.
-  "face" : String. Default to ’arial. Font face (or font family) of the label text.
-  "background" : String. Default to undefined. When not undefined but a
color string, a background rectangle will be drawn behind the label in the
supplied color.
-  "strokeWidth" : Number. Default to 0. As an alternative to the background
rectangle, a stroke can be drawn around the text. When a value higher than
0 is supplied, the stroke will be drawn.
-  "strokeColor" : String. Default to ’#ffffff’. This is the color of the stroke
assuming the value for stroke is higher than 0.
-  "align" : String. Default to ’center’. This can be set to ’left’ to make the
label left-aligned
-  "vadjust, multi, bold, ital, boldital, mono"See visDocumentation
icon : Named list. These options are only used when the shape is set to ’icon’.
-  "face" : String. Default to ’FontAwesome’. These options are only used
when the shape is set to icon. The possible options for the face are: ’FontAwesome’
and ’Ionicons’.
-  "code" : String. Default to undefined. This is the code of the icon, for
example ’\uf007’.
-  "size" : Number. Default to 50. The size of the icon.
-  "color" : String. Default to ’#2B7CE9’. The color of the icon.
shadow : Boolean | named list. Default to false. When true, the node casts a shadow
using the default settings. This can be further refined by supplying a list
-  "enabled" : Boolean. Default to false. Toggle the casting of shadows. If this
option is not defined, it is set to true if any of the properties in this object
are defined.
-  "color" : String. Default to ’rgba(0,0,0,0.5)’. The color of the shadow as
a string. Supported formats are ’rgb(255,255,255)’, ’rgba(255,255,255,1)’
and ’#FFFFFF’.
-  "size" : Number. Default to 10. The blur size of the shadow.
-  "x" : Number. Default to 5. The x offset.
-  "y" : Number. Default to 5. The y offset.
scaling : Named list. If the value option is specified, the size of the nodes will be scaled
according to the properties in this object.
-  "min" : Number. Default to 10. If nodes have a value, their sizes are
determined by the value, the scaling function and the min max values.
visNodes 67
-  "max" : Number. Default to 30. This is the maximum allowed size when
the nodes are scaled using the value option.
-  "label" : Named list or Boolean. Default to Named list. This can be false
if the label is not allowed to scale with the node. If true it will scale using
default settigns. For further customization, you can supply an object.
 - "enabled" : Boolean. Default to false. Toggle the scaling of the label
on or off. If this option is not defined, it is set to true if any of the
properties in this object are defined.
 - "min" : Number. Default to 14. The minimum font-size used for labels
when scaling.
 - "max" : Number. Default to 30. The maximum font-size used for labels
when scaling.
 - "maxVisible" : Number. Default to 30. When zooming in, the font is
drawn larger as well. You can limit the perceived font size using this
option. If set to 30, the font will never look larger than size 30 zoomed
at 100%.
 - "drawThreshold" : Number. Default to 5. When zooming out, the font
will be drawn smaller. This defines a lower limit for when the font is
drawn. When using font scaling, you can use this together with the
maxVisible to first show labels of important nodes when zoomed out
and only show the rest when zooming in.
-  "customScalingFunction" : Function. If nodes have value fields, this function
determines how the size of the nodes are scaled based on their values.
shapeProperties
: Named list. This object contains configuration for specific shapes.
-  "borderDashes" : Vector or Boolean. Default to false. This property applies
to all shapes that have borders. You set the dashes by supplying an Vector
Vector formart: [dash length, gap length]. You can also use a Boolean, false
is disable and true is default [5,15].
-  "borderRadius" : Number. Default to 6. This property is used only for the
box shape. It allows you to determine the roundness of the corners of the
shape.
-  "interpolation" : Boolean. Default to true. This property only applies to the
image and circularImage shapes. When true, the image is resampled when
scaled down, resulting in a nicer image at the cost of computional time.
-  "useImageSize" : Boolean. Default to false. This property only applies to
the image and circularImage shapes. When false, the size option is used,
when true, the size of the image is used.
-  "useBorderWithImage" : Boolean. Default to false. This property only
applies to the image shape. When true, the color object is used. A rectangle
with the background color is drawn behind it and it has a border. This
means all border options are taken into account.
heightConstraint
: See visDocumentation
widthConstraint
: See visDocumentation
68 visOptions
margin : See visDocumentation
chosen : See visDocumentation

#### References

See online documentation http://datastorm-open.github.io/visNetwork/

#### See Also
visNodes for nodes options, visEdges for edges options, visGroups for groups options, visLegend for adding legend, visOptions for custom option, visLayout & visHierarchicalLayout for layout, visPhysics for control physics, visInteraction for interaction, visNetworkProxy & visFocus & visFit for animation within shiny, visDocumentation, visEvents, visConfigure ...

#### Examples

```{r}
nodes <- data.frame(id = 1:3)
edges <- data.frame(from = c(1,2), to = c(1,3))
visNetwork(nodes, edges) %>%
visNodes(shape = "square", title = "I'm a node", borderWidth = 3)
visNetwork(nodes, edges) %>%
visNodes(color = list(hover = "green")) %>%
visInteraction(hover = TRUE)
visNetwork(nodes, edges) %>% visNodes(color = "red")
visNetwork(nodes, edges) %>%
visNodes(color = list(background = "red", border = "blue",
highlight = "yellow"))
visNetwork(nodes, edges) %>% visNodes(shadow = TRUE)
visNetwork(nodes, edges) %>% visNodes(shadow = list(enabled = TRUE, size = 50))
```