---
title: "visnetwork"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(visNetwork)
```
visSave Save a a visNetwork object to an HTML file
#### Description
Save a a visNetwork object to an HTML file for sharing with others. The HTML can include it’s
dependencies in an adjacent directory or can bundle all dependencies into the HTML file (via base64
encoding).
#### Usage
<pre><code>
visSave(graph, file, selfcontained = TRUE, background = "white")
</code></pre>

#### Arguments
* ``graph`` : a visNetwork object
* ``file`` : File to save HTML into. See saveWidget selfcontained : Whether to save the HTML as a single self-contained file (with external resources base64 encoded) or a file with external resources placed in an adjacent directory.
* ``background`` : Text string giving the html background color of the widget. Defaults to white.
#### References
See online documentation http://datastorm-open.github.io/visNetwork/
See Also
visExport
#### Examples
```{r}
## Not run:
nodes <- data.frame(id = 1:3, group = c("B", "A", "B"))
edges <- data.frame(from = c(1,2), to = c(2,3))
network <- visNetwork(nodes, edges)
network
network %>% visSave(file = "network.html", background = "black")
# same as
visSave(network, file = "network.html", background = "black")
```
