---
title: "``visEdges``: Network visualization edges options"
output: html_document
---
 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(visNetwork)
```
visStorePositions Method storePositions, with shiny only.
#### Description
Method storePositions, with shiny only. Put the X and Y positions of all nodes into that dataset.
#### Usage
<pre><code>
visStorePositions(graph)
</code></pre>
#### Arguments
* ``graph`` : a visNetworkProxy object
#### References
See online documentation http://datastorm-open.github.io/visNetwork/
See Also
visNodes for nodes options, visEdges for edges options, visGroups for groups options, visLegend
for adding legend, visOptions for custom option, visLayout & visHierarchicalLayout for layout,
visPhysics for control physics, visInteraction for interaction, visNetworkProxy & visFocus & visFit
for animation within shiny, visDocumentation, visEvents, visConfigure ...
90 visTree
#### Examples
```{r}
## Not run:
# have a look to :
shiny::runApp(system.file("shiny", package = "visNetwork"))
## End(Not run)
