---
title: "``visEdges``: Network visualization edges options"
output: html_document
---
 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(visNetwork)
```
visSetData Network visualization setData method
#### Description
For use setData() method in a shiny app. For full documentation, have a look at visDocumentation.
#### Usage
<pre><code>
visSetData(graph, nodes = NULL, edges = NULL)
</code></pre>
#### Arguments
* ``graph`` : a visNetworkProxy object
nodes : data.frame with nodes informations. Needed at least column "id". See visNodes
* ``edges`` :  data.frame with edges informations. Needed at least columns "from" and "to".
See visEdges

#### Examples
```{r}
## Not run:
# have a look to :
shiny::runApp(system.file("shiny", package = "visNetwork"))
```

#### References
See online documentation http://datastorm-open.github.io/visNetwork/
See Also
visNodes for nodes options, visEdges for edges options, visGroups for groups options, visLegend
for adding legend, visOptions for custom option, visLayout & visHierarchicalLayout for layout,
visPhysics for control physics, visInteraction for interaction, visNetworkProxy & visFocus & visFit
for animation within shiny, visDocumentation, visEvents, visConfigure ...
