---
title: "visnetwork"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(visNetwork)
```

visSelectEdges Function to select edge(s) from network, with shiny only.
#### Description
Function to select edges(s) from network, with shiny only.
#### Usage
<pre><code>
visSelectEdges(graph, id)
</code></pre>
#### Arguments
* ``graph`` : a visNetworkProxy object
id : vector of id, edges(s) to select
#### References
See online documentation http://datastorm-open.github.io/visNetwork/
See Also
visNodes for nodes options, visEdges for edges options, visGroups for groups options, visLegend
for adding legend, visOptions for custom option, visLayout & visHierarchicalLayout for layout,
visPhysics for control physics, visInteraction for interaction, visNetworkProxy & visFocus & visFit
for animation within shiny, visDocumentation, visEvents, visConfigure ...
#### Examples
```{r}
## Not run:
# have a look to :
shiny::runApp(system.file("shiny", package = "visNetwork"))
```
visSelectNodes Function to select node(s) from network, with shiny only.
#### Description
Function to select node(s) from network, with shiny only.
#### Usage
<pre><code>
visSelectNodes(graph, id, highlightEdges = TRUE, clickEvent = TRUE)
</code></pre>
#### Arguments
* ``graph`` : a visNetworkProxy object
* ``id`` : vector of id, node(s) to select
* ``highlightEdges`` : Boolean. highlight Edges also ? Default to TRUE
* ``clickEvent`` : Boolean. Launch click event ? (highlightNearest for example) Default to TRUE
#### References
See online documentation http://datastorm-open.github.io/visNetwork/
See Also
visNodes for nodes options, visEdges for edges options, visGroups for groups options, visLegend
for adding legend, visOptions for custom option, visLayout & visHierarchicalLayout for layout,
visPhysics for control physics, visInteraction for interaction, visNetworkProxy & visFocus & visFit
for animation within shiny, visDocumentation, visEvents, visConfigure ...
#### Examples
```{r}
## Not run:
# have a look to :
shiny::runApp(system.file("shiny", package = "visNetwork"))
## End(Not run)
```
