---
title: "``visEdges``: Network visualization edges options"
output: html_document
---
 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(visNetwork)
```


visTree Visualize Recursive Partitioning and Regression Trees (rpart object)
#### Description
Visualize Recursive Partitioning and Regression Trees rpart. Have a look to visTreeEditor to edity
and get back network, or to visTreeModuleServer to use custom tree module in R
#### Usage
<pre><code>
visTree(object, data = NULL, tooltipColumns = if (!is.null(data)) {
1:ncol(data) } else { NULL }, main = "", submain = "", footer = "",
direction = "UD", fallenLeaves = FALSE, rules = TRUE,
simplifyRules = TRUE, shapeVar = "dot", shapeY = "square",
colorVar = NULL, colorY = NULL, colorEdges = "#8181F7",
nodesFontSize = 16, edgesFontSize = 14, edgesFontAlign = "horizontal",
legend = TRUE, legendNodesSize = 22, legendFontSize = 16,
legendWidth = 0.1, legendNcol = 1, legendPosition = "left",
nodesPopSize = FALSE, minNodeSize = 15, maxNodeSize = 30,
highlightNearest = list(enabled = TRUE, degree = list(from = 50000, to = 0),
hover = FALSE, algorithm = "hierarchical"), collapse = list(enabled = TRUE,
fit = TRUE, resetHighlight = TRUE, clusterOptions = list(fixed = TRUE, physics
= FALSE)), updateShape = TRUE, tooltipDelay = 500, digits = 3,
height = "600px", width = "100%", export = TRUE)
</code></pre>
#### Arguments
object rpart, rpart object
data data.frame, adding mini-graphics in tooltips using sparkline and tooltipColumns
?
tooltipColumns numeric, indice of columns used in tooltip. All by default. So, we add boxplot
/ pie focus on sub-population vs all population using sparkline package. NULL
to disable.
main Title. See visNetwork
submain Subtitle. See visNetwork
footer Footer. See visNetwork
visTree 91
direction character, The direction of the hierarchical layout. The available options are:
UD, DU, LR, RL. To simplify: up-down, down-up, left-right, right-left. Default
UD. See visHierarchicalLayout
fallenLeaves boolean leaf nodes at the bottom of the graph ? Default to FALSE
rules boolean, add rules in tooltips ? Default to TRUE
simplifyRules boolean, simplify rules writing
shapeVar character, shape for variables nodes See visNodes
shapeY character, shape for terminal nodes See visNodes
colorVar character, colors to use or data.frame To set color of variables. 2 columns :
-  "variable" : names of variables
-  "color" : colors (in hexa). See examples
colorY if classification tree : character colors to use or data.frame 2 columns :
-  "modality" : levels of Y
-  "color" : colors (in hexa)
if regression tree : character, 2 colors (min and max, in hexa)
colorEdges character, color of edges, in hexa. Default to #8181F7
nodesFontSize numeric, size of labels of nodes. Default to 16
edgesFontSize numeric, size of labels of edges Default to 14
edgesFontAlign character, for edges only. Default tp ’horizontal’. Possible options: ’horizontal’
(Default),’top’,’middle’,’bottom’. See visEdges
legend boolean, add legend ? Default TRUE. visLegend
legendNodesSize
numeric, size of nodes in legend. Default to 22
legendFontSize numeric, size of labels of nodes in legend. Default to 16
legendWidth numeric, legend width, between 0 and 1. Default 0.1
legendNcol numeric, number of columns in legend. Default 1
legendPosition character, one of "left" (Default) or "right"
nodesPopSize boolean, nodes sizes depends on population ? Default to FALSE
minNodeSize numeric, in case of nodesPopSize, minimum size of a node. Defaut to 15. Else,
nodes size is minNodeSize + maxNodeSize / 2
maxNodeSize numeric, in case of nodesPopSize, maximum size of a node. Defaut to 30.
Else, nodes size is minNodeSize + maxNodeSize / 2
highlightNearest
list, Highlight nearest nodes. See visOptions
collapse list, collapse or not using double click on a node ? See visOptions
updateShape boolean, in case of collapse, udpate cluster node shape as terminal node ? Default
to TRUE
tooltipDelay numeric, delay for tooltips in millisecond. Default 500
digits numeric, number of digits. Default to 3
* ``height`` :    character, default to "600px"
* ``width `` :  character, default to "100%"
* ``export`` :  boolean, add export button. Default to TRUE
92 visTree
Value
a visNetwork object
#### References
See online documentation http://datastorm-open.github.io/visNetwork/
See Also
visTreeEditor, visTreeModuleServer, visNetworkEditor
#### Examples
```{r}
## Not run:
library(rpart)
# Basic classification tree
res <- rpart(Species~., data=iris)
visTree(res, data = iris, main = "Iris classification Tree")
# Basic regression tree
res <- rpart(Petal.Length~., data=iris)
visTree(res, edgesFontSize = 14, nodesFontSize = 16)
# Complex tree
data("solder")
res <- rpart(Opening~., data = solder, control = rpart.control(cp = 0.00005))
visTree(res, data = solder, nodesPopSize = TRUE, minNodeSize = 10,
maxNodeSize = 30, height = "800px")
# ----- Options
res <- rpart(Opening~., data = solder, control = rpart.control(cp = 0.005))
# fallen leaves + align edges label & size
visTree(res, fallenLeaves = TRUE, height = "500px",
edgesFontAlign = "middle", edgesFontSize = 20)
# disable rules in tooltip, and render tooltip faster
# enable hover highlight
visTree(res, rules = FALSE, tooltipDelay = 0,
highlightNearest = list(enabled = TRUE, degree = list(from = 50000, to = 0),
hover = TRUE, algorithm = "hierarchical"))
# Change color with data.frame
colorVar <- data.frame(variable = names(solder),
color = c("#339933", "#b30000","#4747d1","#88cc00", "#9900ff","#247856"))
colorY <- data.frame(modality = unique(solder$Opening),
color = c("#AA00AA", "#CDAD15", "#213478"))
visTreeEditor 93
visTree(res, colorEdges = "#000099", colorVar = colorVar, colorY = colorY)
# Change color with vector
visTree(res, colorEdges = "#000099",
colorVar = substring(rainbow(6), 1, 7),
colorY = c("blue", "green", "orange"))
# Use visNetwork functions to add more options
visTree(res) %>%
visOptions(highlightNearest = TRUE)
## End(Not run)
