
---
title: "``visNetwork::visUpdateNodes``"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(visNetwork)
```


visUpdateNodes Function to update the information of nodes, with shiny only.
#### Description
Function to update the information of nodes, with shiny only. You can also use this function passing
new nodes. The link is based on id.

#### Usage
<pre><code>
visUpdateNodes(graph, nodes, updateOptions = TRUE, legend = FALSE)
</code></pre>
#### Arguments
* ``graph`` : a visNetworkProxy object
* ``nodes`` :  data.frame with the information of nodes. Needed at least column "id". See
visNodes
-  "id" : id of the node, needed in the definition of edges and for update nodes
-  "label" : label of the node
-  "group" : group of the node. Groups can be configure with visGroups
-  "value" : size of the node
-  "title" : tooltip of the node
-  ...
updateOptions : Boolean. Update options (nodesIdSelection & selectedBy) if needed ? Default
to TRUE.
* ``legend`` :   Boolean. Update nodes on legend ? Default to FALSE

#### Examples
```{r}
## Not run:
# have a look to :
shiny::runApp(system.file("shiny", package = "visNetwork"))
## End(Not run)
```
#### References
See online documentation http://datastorm-open.github.io/visNetwork/
