---
title: "``visClusteringByGroup``"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(visNetwork)
```
 Network visualization clustering options - by group

#### Description
Network visualization clustering options - by group.
#### Usage
<pre><code>
visClusteringByGroup(graph, groups, label = "Cluster on group : ",
shape = "database", color = "grey", force = FALSE, scale_size = TRUE)
</code></pre>

#### Arguments
* ``graph`` : a visNetwork object
* groups : Character/vector. groups we want to cluster
*``label`` : Character. Label put before value(s). See example
*``shape`` : Character.Shape of cluster(s) if different shapes between nodes or force = T. "database" per default
* color : Character. Color of cluster(s) if different colors between nodes or force = T. "grey" per default
* force : If force = FALSE, Set shape and color of nodes if all equal, else directly
defaut shape and color
* scale_size : Set size based on cluster population ? Default to TRUE.

#### Examples

```{r}
nodes <- data.frame(id = 1:10, label = paste("Label", 1:10),
group = sample(c("A", "B"), 10, replace = TRUE))
edges <- data.frame(from = c(2,5,10), to = c(1,2,10))
visNetwork(nodes, edges) %>%
visGroups(groupname = "A", color = "red", shape = "database") %>%
visGroups(groupname = "B", color = "yellow", shape = "triangle") %>%
visClusteringByGroup(groups = c("B"), label = "Group : ",
shape = "ellipse", color = "blue", force = TRUE) %>%
visLegend()
```
